---
title: "Assignment 4"
author: "Alvaro Guijarro"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Assignment 4

Loading the necessary libraries

```{r warning=FALSE, message=FALSE}
library(dplyr)
library(knitr)
```

Define the path for the original datasets to access, add year & party columns, and clean them:
```{r}
base_path <- "C:/Users/alvar/OneDrive/Documents/GitHub/text-as-data-assignments/data"
democrats_2012 <- read.csv(file.path(base_path, "Democrats_2012_11.csv"))
democrats_2016 <- read.csv(file.path(base_path, "Democrats_2016_11.csv"))
democrats_2020 <- read.csv(file.path(base_path, "Democrats_2020_11.csv"))
republicans_2012 <- read.csv(file.path(base_path, "Republicans_2012_11.csv"))
republicans_2016 <- read.csv(file.path(base_path, "Republicans_2016_11.csv"))
republicans_2020 <- read.csv(file.path(base_path, "Republicans_2020_11.csv"))

democrats_2012$Election <- '2012_11'
democrats_2016$Election <- '2016_11'
democrats_2020$Election <- '2020_11'
democrats_2012$Party <- 'Democrats'
democrats_2016$Party <- 'Democrats'
democrats_2020$Party <- 'Democrats'

republicans_2012$Election <- '2012_11'
republicans_2016$Election <- '2016_11'
republicans_2020$Election <- '2020_11'
republicans_2012$Party <- 'Republicans'
republicans_2016$Party <- 'Republicans'
republicans_2020$Party <- 'Republicans'
```

Merge all datasets into one and view the combined dataset:
```{r, warning=FALSE}
all_data <- rbind(democrats_2012, democrats_2016, democrats_2020, republicans_2012, republicans_2016, republicans_2020)
knitr::kable(head(all_data, 10), caption = "First 10 Rows of the Combined Dataset")
```

**#Question 1**

"1. Data acquisition, description, and preparation
Bring together a dataset from the WZB.
What years, countries and parties are included in the dataset? How many texts do you have for each of these?
Prepare your data for topic modelling by creating a document feature matrix. Describe the choices you make
here, and comment on how these might affect your final result."

```{r echo=FALSE, message=FALSE}
# Group by Party and Election, then summarize
summary_table <- all_data %>%
  group_by(Party, Election) %>%
  summarize(
    Total_Entries = n(), # Count total number of entries
    Unique_Topics = length(unique(cmp_code)) # Count unique cmp_code values
  ) %>%
  ungroup() # Remove the grouping

# Display the table in R Markdown
knitr::kable(summary_table, caption = "Summary of Data by Party and Election of USA ", format = "markdown")
```

```{r}

```
